---
title: "Machine Learning Assignment 4"
date: "2022-10-16"
output: html_document
---


```{r}
library(ISLR)
library(MASS)
library(boot)
```


1.	We continue to consider the use of a logistic regression model to predict the probability 
	Of  default using income and balance on the Default data set. In particular, we will now 
compute estimates for the standard errors of the income and balance logistic regression
 coefficients in two different ways: (1) using the bootstrap, and (2) using the standard 
formula for computing the standard errors in the glm() function. Do not forget to set a 
random seed before beginning your analysis

(a) Using the summary() and glm() functions, determine the estimated standard errors for the coefficients associated with income and balance in a multiple logistic regression model that uses both predictors.


```{r}
set.seed(1)
attach(Default)
```

```{r}
glm.fit = glm(default ~ income + balance, data = Default, family = "binomial")
summary(glm.fit)
```

Ans:
  The estimated standard errors of the coefficients are listed income is 4.985e-06 balance is 2.274e-04
  
  

(b) Write a function, boot.fn(), that takes as input the Default data set as well as an index of the observations, and that outputs the coefficient estimates for income and balance in the multiple logistic regression model.  
  
```{r}
library(boot)
```


```{r}
boot.fn = function(data, index){
  return(coef(glm(default~income+balance, data=Default, family="binomial", subset=index)))  
}
boot.fn(Default, 1:nrow(Default))
```
  
Ans:
  the boot function return the coefficient value and income is 2.080898e-05 balance is 5.647103e-03
  
  

 (c) Use the boot() function together with your boot.fn() function to estimate the standard errors of the logistic regression coefficients for “income” and “balance”.
 
 
```{r}
boot(Default, boot.fn, 1000)
```

Ans:
  The bootstrap estimates of the standard errors for the coefficients income 4.866284e-06
balance 2.298949e-04
  
  
 (d) Comment on the estimated standard errors obtained using the glm() function and using your bootstrap function.
 
 Ans:
 
 
 
2.we saw that the cv.glm() function can be used in order to compute the LOOCV test error 
	estimate. Alternatively, one could compute those quantities using just the glm() and 
	predict.glm() functions, and a for loop. You will now take this approach in order to 
	compute the LOOCV error for a simple logistic regression model on the Weekly data set. 
	
(a) Fit a logistic regression model that predicts Direction using Lag1 and Lag2.


```{r}
set.seed(1)
Weekly
```

```{r}
glm.fit.1 = glm(Direction ~ Lag1 + Lag2, data=Weekly, family="binomial")
summary(glm.fit.1)
```

Ans:
  find glm() function for the variable Lag1 and Lag2.
  
  
  
 (b).Fit a logistic regression model that predicts Direction using Lag1 and Lag2 using all but the first observation.
 
```{r}
glm.fit2 = glm(Direction ~ Lag1 + Lag2, data=Weekly[-1, ], family="binomial")
summary(glm.fit2)
```

Ans:
  find glm() function for the variable Lag1 and Lag2 and include the first column by LOOCV method.
  
  
(c) Use the model from (b) to predict the direction of the first observation. You can do this by predicting that the first observation will go up if P(Direction="Up"|Lag1, Lag2) > 0.5. Was this observation correctly classified?


```{r}
predict(glm.fit2, Weekly[1, ], type="response")>0.5
```

```{r}
Weekly[1,]$Direction
```

Ans:
  this observation was not correctly classified as the true direction is Down so first value is wrong
  
  
(d) Write a for loop from i = 1 to i = n, where n is the number of observations in the data set, that performs each of the following steps:

 i. Fit a logistic regression model using all but the ith observation to predict Direction using Lag1 and Lag2.
 
  ii. Compute the posterior probability of the market moving up for the ith observation. 
iii. Use the posterior probability for the ith observation in order to predict whether or not the market moves up. 

iv. Determine whether or not an error was made in predicting the direction for the ith observation. If an error was made, then indicate this as a 1, and otherwise indicate it as a 0.

```{r}
error <- rep(0, nrow(Weekly))
for (i in 1:nrow(Weekly)){
 fit =  glm(Direction ~ Lag1+Lag2, data=Weekly[-i, ], family=binomial)
 pred = predict(fit, Weekly[i, ], type="response") > 0.5
 true <- Weekly[i, ]$Direction == "Up"
 if (pred != true)
   error[i] = 1
}
pred
true
error
```

Ans:
   we use the loop and check three value for all values column is true and the error row value has changed to 0 and 1 this true or false

 (e) Take the average of the n numbers obtained in (d)iv in order to obtain the LOOCV estimate for the test error. Comment on the results
 
```{r}
mean(error)
```

